\documentclass[a4paper,12pt,twoside]{report}

\usepackage{xunicode}
\usepackage{xltxtra}
\usepackage{hyperref}
\usepackage{fontspec}
\setmainfont[Mapping=tex-text,Ligatures={Common,Rare,Discretionary}]{Linux Libertine O}

\usepackage{pdflscape}

\usepackage{enumitem}


\usepackage{polyglossia}
\setdefaultlanguage{spanish}
\setotherlanguage{english}

\usepackage{listings}
\usepackage{color}

\definecolor{gray}{rgb}{0.4,0.4,0.4}
\definecolor{darkblue}{rgb}{0.0,0.0,0.6}
\definecolor{cyan}{rgb}{0.0,0.6,0.6}

\lstset{
  basicstyle=\ttfamily,
  columns=fullflexible,
  showstringspaces=false,
  commentstyle=\color{gray}\upshape
}

\lstdefinelanguage{XML}
{
  morestring=[b]",
  morestring=[s]{>}{<},
  morecomment=[s]{<?}{?>},
  stringstyle=\color{black},
  identifierstyle=\color{darkblue},
  keywordstyle=\color{cyan},
  morekeywords={xmlns,version}% list your attributes here
}

\pagestyle{headings}

\author{Óscar González Fernández}
\title{DARE: Distributed aAutomator Runtime Environment}
\begin{document}
\maketitle
\tableofcontents
\chapter{Memoria}
\input{chapters/memoria.tex}
\chapter{Manual técnico}
\input{chapters/technical-manual.tex}
\chapter{Manual usuario}
\input{chapters/user-manual.tex}

\begin{thebibliography}{1}

\bibitem{aAUTOMATOR}
  D. Glez-Peña, J.R. Méndez, F. Fdez-Riverola (2007)
  \newblock \emph{aAUTOMATOR}: Herramienta Flexible Para La
  Extracción De Información En Sitios Web Bioinformáticos. Vila Real,
  Portugal. 07 - octubre
\bibitem{DSL}
  Martin Fowler
  \newblock Domain-Specific Languages
  \newblock ISBN 978-0-321-71294-3
\bibitem{RUBY}
  David Thomas, Andrew Hunt.
  \newblock Programming Ruby: the pragmatic programmer's guide
  \newblock ISBN 0201710897
\bibitem{REST}
  Roy Fielding
  \newblock Architectural Styles and
  the Design of Network-based Software Architectures
  \newblock
  \url{http://www.ics.uci.edu/~fielding/pubs/dissertation/top.htm},
  2012.
\bibitem{JAXRS}
  \newblock JSR 311: JAX-RS: The JavaTM API for RESTful Web Services
  \newblock \url{http://jcp.org/en/jsr/detail?id=311}, 2012.
\bibitem{JOY}
  Michael Fogus, Chris Houser.
  \newblock The Joy of Clojure: Thinking the Clojure Way
  \newblock ISBN 1935182641
\bibitem{FUNCTIONAL}
  \newblock Functional programming
  \newblock \url{http://en.wikipedia.org/wiki/Functional_programming}, 2012.
\bibitem{LISP}
  \newblock Lisp programming language
  \newblock \url{http://en.wikipedia.org/wiki/Lisp_(programming_language)}, 2012.
\bibitem{MONGO}
  \newblock MongoDB
  \newblock \url{http://www.mongodb.org/}, 2012.
\bibitem{NOSQL}
  \newblock NoSQL
  \newblock \url{http://www.mongodb.org/}, 2012.
\bibitem{DEVOPS}
  \newblock DevOps
  \url{http://en.wikipedia.org/wiki/Devops}, 2012.
\bibitem{JCLOUDS}
  \newblock jclouds
  \newblock \url{http://www.jclouds.org/}, 2012.
\bibitem{PALLET}
  \newblock Pallet, DevOps for the JVM
  \newblock \url{http://palletops.com/}, 2012.
\bibitem{JETTY}
  \newblock Jetty
  \newblock \url{http://www.eclipse.org/jetty/}, 2012.
\bibitem{UML}
  Grady Booch, Ivar Jacobson \& Jim Rumbaugh
  \newblock The Unified Modeling Language User Guide
\bibitem{SOUP}
  \newblock Beatiful Soup
  \newblock \url{http://www.crummy.com/software/BeautifulSoup/}, 2012.
\bibitem{MECHANIZE}
  \newblock WWW::Mechanize
  \newblock
  \url{http://search.cpan.org/~jesse/WWW-Mechanize-1.72/lib/WWW/Mechanize.pm},
  2012.
\bibitem{HPRICOT}
  \newblock Hpricot
  \newblock \url{http://hpricot.com/}, 2012.
\bibitem{MASHUP}
  \newblock Mashup
  \newblock \url{http://en.wikipedia.org/wiki/Mashup_(web_application_hybrid)}, 2012.
\bibitem{DAG}
  \newblock Directed acyclic graph
  \newblock \url{http://en.wikipedia.org/wiki/Directed_acyclic_graph},
  2012..
\bibitem{PYTHON}
  \newblock Python
  \newblock
  \url{http://en.wikipedia.org/wiki/Python_(programming_language)}, 2012.
\bibitem{UNIX}
  \newblock Unix
  \newblock \url{http://en.wikipedia.org/wiki/Unix}, 2012.
\bibitem{MIME}
  \newblock Media Type
  \newblock \url{http://en.wikipedia.org/wiki/Media_type}, 2012.
\bibitem{SOAP}
  \newblock SOAP
  \newblock \url{http://en.wikipedia.org/wiki/SOAP}, 2012.
\bibitem{JERSEY}
  \newblock Jersey
  \newblock \url{http://jersey.java.net/}, 2012.
\bibitem{BSON}
  \newblock BSON
  \newblock \url{http://en.wikipedia.org/wiki/BSON}, 2012.
\bibitem{MAP-REDUCE}
  \newblock Map Reduce
  \newblock \url{http://en.wikipedia.org/wiki/Map_reduce}, 2012.
\bibitem{SHARDING}
  \newblock Sharding
  \newblock \url{http://en.wikipedia.org/wiki/Sharding}, 2012.
\bibitem{MASTER-SLAVE}
  \newblock Replicación \emph{master-slave}
  \newblock
  \url{http://dev.mysql.com/doc/refman/5.0/en/replication.html}, 2012.
\bibitem{BIG-TABLE}
  Fay Chang, Jeffrey Dean, Sanjay Ghemawat, Wilson C. Hsieh, Deborah A. Wallach, Mike Burrows, Tushar Chandra, Andrew Fikes, and Robert E. Gruber.
  \newblock Bigtable: A Distributed Storage System for Structured Data
  \newblock OSDI'06: Seventh Symposium on Operating System Design and
  Implementation. November, 2006.
\bibitem{HADOOP}
  \newblock Apache Hadoop
  \newblock \url{http://en.wikipedia.org/wiki/Apache_Hadoop}, 2012.
\bibitem{CLR}
  \newblock Common Language Runtime.
  \newblock
  \url{http://en.wikipedia.org/wiki/Common_Language_Runtime}, 2012.
\bibitem{PERSISTENT-DATA-STRUCTURES}
  \newblock Persistent data structure
  \newblock
  \url{http://en.wikipedia.org/wiki/Persistent_data_structure}, 2012.
\bibitem{CONGO-MONGO}
  \newblock CongoMongo
  \newblock \url{https://github.com/aboekhoff/congomongo}, 2012.
\bibitem{FRP}
  \newblock Functional Reactive Programming
  \newblock
  \url{http://en.wikipedia.org/wiki/Functional_reactive_programming}, 2012.
\bibitem{EMBARRASSINGLY-PARALLEL}
  \newblock Embarrassingly Parallel
  \newblock \url{http://en.wikipedia.org/wiki/Embarrassingly_parallel}, 2012.
\bibitem{MASTER-WORKER}
  \newblock Distributed Computing Made Easy
  \newblock
  \url{http://www.theserverside.com/news/1365083/Distributed-Computing-Made-Easy},
  2012.
\bibitem{SQLite}
  \newblock SQLite
  \newblock \url{http://www.sqlite.org/}, 2012.
\bibitem{COMPOSITE_PATTERN}
  \newblock Patrón Composite
  \newblock \url{http://en.wikipedia.org/wiki/Composite_pattern},
  2012.
\bibitem{METAPROGRAMMING}
  \newblock Metaprogramación
  \newblock \url{http://en.wikipedia.org/wiki/Metaprogramming}, 2012.
\end{thebibliography}
\end{document}
